Comparison of simulation to theory

### 2016-02-25 sims/compare-to-theory.Rmd
mean hap lengths works?

We'll do this against $x$ at a few values of $r$ because that's what we have.
```{r theory_haps, cache=TRUE}
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=41)
hap.soln <- forwards_backwards_haplotypes(s=theory.params$s, times=tt, xgrid=xgrid, rgrid=rgrid,
                           sigma=theory.params$sigma, 
                           fwds.grid=fgrid, fwds.soln=fwds.soln )
```

>>>>

We'll do this against $x$ at a few values of $r$ because that's what we have.
(Don't mess with this next code chunk, it'll invalidate the cache, which was expensive to make.)
```{r theory_haps, cache=TRUE}
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=41)
hap.soln <- forwards_backwards_haplotypes(s=theory.params$s, times=tt, xgrid=xgrid, rgrid=rgrid,
                           sigma=theory.params$sigma, 
                           fwds.grid=fgrid, fwds.soln=fwds.soln )
```

Now let's compare this to simulation:
```{r sim_hap_lens}
sim_lens <- sapply( chunks, sapply, mean )
sim_cond_lens <- sapply( chunks, sapply, function (x) { if (any(x>0)) { mean(x[x>0]) } else { NA } } )

hap.len.mat <- sapply( chunks.rvals, function (crv) { 
               haplens <- mean_hap_len( hap.soln, loc=if(crv[1]==1){crv[2]-0.5}else{max(rgrid$x.mid)} ) 
               haplens[length(tt),1+seq_along(xgrid$x.mid)]
           } )

matplot(xx, sim_lens, type='l', lty=sapply(chunks.rvals,"[",1),
        main="mean haplotype length",
        xlab="spatial position", ylab="mean B haplotype length (incl. zeros)")
matlines( rev(xgrid$x.mid), hap.len.mat, lty=3 )
legend("topleft", lty=c(sapply(chunks.rvals,"[",1),3), col=c(rep_len(1:6,ncol(sim_cond_lens)),1),
        legend=c( sapply( chunks.rvals, function (x) { sprintf("chr %d: %0.3f",x[1],x[2]) } ), "theory") )
```

```{r get_mean_hap_lens}
hap.pdf <- hap_cdf_to_pdf( hap.soln )
```

Here are haplotype probabilities (**not** cumulative):
```{r look_at_haps}
for (haplen in c(0.02, 0.04, 0.08, 0.16, 0.32) ) {
    hap.probs <- get_hap_probs( hap.pdf, left=-haplen/2, right=haplen/2 )
    image(hap.probs, legend=TRUE, yaxt='n',
       main=paste(c("A:","B:"),paste(round(attr(hap.probs,"r"),3),collapse=" to ")) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
}
```
and here are the same offset by `r rgrid$dx[1]`
```{r look_at_haps_offset}
for (haplen in c(0.02, 0.04, 0.08, 0.16, 0.32) ) {
    hap.probs <- get_hap_probs( hap.pdf, left=rgrid$dx[1], right=rgrid$dx[1]+haplen )
    image(hap.probs, legend=TRUE, yaxt='n',
       main=paste(c("A:","B:"),paste(round(attr(hap.probs,"r"),3),collapse=" to ")) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
}
```

Here are also heatmaps of **mean lengths**:
```{r hap_lens}
hap.centers <- c(0.0, 0.02, 0.04, 0.08, 0.16, 0.32)
for (kloc in seq_along(hap.centers)) {
    hap.len <- mean_hap_len( hap.pdf, loc=hap.centers[kloc] )
    image(hap.len, legend=TRUE, yaxt='n',
          main=paste(c("A:","B:"),sprintf("mean haplotype length at %f",hap.centers[kloc])) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
}
```
